### 2018-07-09 FrascatiPlot/Paper/NucleiB2.tex
adding first version complete version of chapter 4.2

In figure~\ref{fig:CompareThermalAndCoalescence}, the data available data for (anti-)deuteorns, (anti)\hethree\ and \hthreelambda~\cite{Adam:2015yta} is compared to both coalescence and thermal model predictions. For the coalescence predictions, the radius parameterisation tuned to the data is used. The combined thermal model and blast-wave predictions are calculated as described in section~\ref{sec:thermal}. For deuterons and \hethree\ both approaches lead to similar to similar predictions and give a reasonable description of the experimental data.

 - add a three-panel plot for deuteron, he and hyper-triton with different radii for hyper-triton from 10fm to 3fm and for the excited state of the hyper-triton!!

\begin{figure}[htbp]
	\begin{center}
		\includegraphics[width=\textwidth]{compareThermalAndCoalescence.png}
		\caption{Comparison of the ALICE data from~\cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017} with the thermal model expectations and the coalescence prediction which is tuned to \btwo\ values in central Pb-Pb collisions.}
		\label{fig:CompareThermalAndCoalescence}
	\end{center}
\end{figure}
 %\subsection{Predictions for A=4}
 %- add a plot for A=4

@@

In a follow-up publication, we will extend the study presented here to predictions for the $A$=4 systems introduced in Tab.~\ref{table} and to more exotic QCD objects like the X(3827). These predictions will be of outmost importance for the currently prepared physics case for LHC Run 3 \& 4 and beyond.

>>>>

In figure~\ref{fig:CompareThermalAndCoalescence}, the data available data for (anti-)deuteorns, (anti)\hethree\ and \hthreelambda~\cite{Adam:2015yta} is compared to both coalescence and thermal model predictions. For the coalescence predictions, the radius parameterisation tuned to the data is used. The combined thermal model and blast-wave predictions are calculated as described in section~\ref{sec:thermal}. As a first observation, one sees that for deuterons and \hethree\ both approaches lead to similar predictions and give a reasonable description of the experimental data. However, both approaches show large differences for the \hthreelambda\ caused by the significantly larger size of  \hthreelambda\ with respect to \hethree. As a matter of fact, the only available data point so far shows a better agreement with the thermal+BW model than with the coalescence model. However, some authors argue that the difference to the coalescence model might be explained by a later formation through $\Lambda$s and deuterons~\cite{Zhang:2018euf}. In addition, the presence of an excited state with $J=3/2$ of the hyper-triton would significantly enhance the phase space for its production which is not considered here as there is no evidence for its existence~\cite{Mart:1996ay}. The determination of the exact potential enhancement factor is beyond the scope of this paper as it requires at least a rough knowledge of the wave-function, but a factor of two would be expected from counting the spin states.

\begin{figure}[htbp]
	\begin{center}
		\includegraphics[width=\textwidth]{compareThermalAndCoalescence.png}
		\caption{Comparison of the ALICE data from~\cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017} with the thermal model expectations and the coalescence prediction which is tuned to \btwo\ values in central Pb-Pb collisions.}
		\label{fig:CompareThermalAndCoalescence}
	\end{center}
\end{figure}

Figure~\ref{fig:CompareThermalAndCoalescence} also shows most importantly that the difference between the two approaches increases with decreasing source volume, thus underlining the need for additional and more precise data as a function of multiplicity and collision centrality in order to distinguish the two production scenarios. This behaviour also highlights the unique potential to constrain the wave-function of the particle under study at the moment of its production.

 - add an estimate for the hyper-triton in pp collisions

 %\subsection{Predictions for A=4}
 %- add a plot for A=4

@@

In a follow-up publication, we will extend the study presented here to predictions for the $A$=4 systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3827). These predictions will be of outmost importance for the currently prepared physics case for LHC Run 3 \& 4 and beyond.
